### 2014-12-10 docs/ms.Rmd
Updated some mnor bugs in the analysis script which prevented the proper caluclation of some percentages. Also added into analysis the new code and data deposition data collected by Tom.

Of the `r nrow(coldat)` studies analysed, (PERCENTAGE)% publicly provided the raw underlying data, (PERCENTAGE)% provided data in a pre-processed form, and (PERCENTAGE)% of studies did not provide any publicly accessible data. The paucity of data being made available post-publication in studies of biological colouration is in line with other fields [@drew_lost_2013; @vines_mandated_2013; @wolkovich_advances_2012], including the broader field of animal behaviour [@caetano_forgotten_2014]. There is evidence, however, that this trend is shifting as funders and journals increasingly mandate the release of data [@whitlock_data_2010]. The clearest benefit of open access to data is that it allows researchers to build upon previous work for the testing and refinement of new ideas and methods. This is particularly relevant in the study of colour traits, where new methods for analysing colour data are regularly developed [e.g. @allen_analyzing_2013; @endler_framework_2012; @stoddard_pattern_2014]. The provision of open data may also foster collaborations as researchers draw upon existing work [@whitlock_data_2011], and increased data sharing has been shown to positively correlate with citations [@piwowar_sharing_2007]. Given the increasing rate of retractions, there is also impetus for researchers to maintain credibility through transparency [@steen_retractions_2010; @van_trouble_2011; @wicherts_willingness_2011]. We thus encourage researchers to publicly archive data in as raw a form as possible (e.g. individual reflectance spectra), to maximise its utility. Public data repositories such as figshare (REF?) and dryad (REF?) facilitate the permanent archival of data as citable research objects, and the preparation of data for publication is often straightforward [@whitlock_data_2011]. The use of modest data embargoes and appropriate licenses can help to ensure that original authors are able to make the best use of data, and are subsequently credited [though we acknowledge that tensions over data-sharing exist; discussed in @roche_troubleshooting_2014].

>>>>

Of the `r nrow(coldat)` studies analysed, `r round((data["raw"]/sum(data))*100, digits = 2)`% publicly provided the raw underlying data, `round((data["proc"]/sum(data))*100, digits = 2)`% provided data in a pre-processed form, and `r round((data["none"]/sum(data))*100, digits = 2)`% of studies did not provide any publicly accessible data. The paucity of data being made available post-publication in studies of biological colouration is in line with other fields [@drew_lost_2013; @vines_mandated_2013; @wolkovich_advances_2012], including the broader field of animal behaviour [@caetano_forgotten_2014]. There is evidence, however, that this trend is shifting as funders and journals increasingly mandate the release of data [@whitlock_data_2010]. The clearest benefit of open access to data is that it allows researchers to build upon previous work for the testing and refinement of new ideas and methods. This is particularly relevant in the study of colour traits, where new methods for analysing colour data are regularly developed [e.g. @allen_analyzing_2013; @endler_framework_2012; @stoddard_pattern_2014]. The provision of open data may also foster collaborations as researchers draw upon existing work [@whitlock_data_2011], and increased data sharing has been shown to positively correlate with citations [@piwowar_sharing_2007]. Given the increasing rate of retractions, there is also impetus for researchers to maintain credibility through transparency [@steen_retractions_2010; @van_trouble_2011; @wicherts_willingness_2011]. We thus encourage researchers to publicly archive data in as raw a form as possible (e.g. individual reflectance spectra), to maximise its utility. Public data repositories such as figshare (REF?) and dryad (REF?) facilitate the permanent archival of data as citable research objects, and the preparation of data for publication is often straightforward [@whitlock_data_2011]. The use of modest data embargoes and appropriate licenses can help to ensure that original authors are able to make the best use of data, and are subsequently credited [though we acknowledge that tensions over data-sharing exist; discussed in @roche_troubleshooting_2014].
